### 2020-06-19 README.Rmd
codecov token Readme cleaning

``` r
# install.packages("devtools")
devtools::install_github("antaldaniel/eurobarometer")
```

@@

## Joining Serveral Files

The vocabulary functions help to create data panels across Eurobarometer surveys taken in different times.

There are two main issues that need to be resolved in such cases

*  Make sure that the same questions are used, and they are consistently named (this problem is treated in the metadata level)

* In case of structured questions or question blocks the answer options are coded exactly the same (for example “Fully agree”and “Totally agree” are the same.) This will be handled by the vocabulary functions. (Not yet implemented.)

>>>>

``` r
# install.packages("devtools")
devtools::install_github("antaldaniel/eurobarometer")
```
## Workflow

Not all elements of the [Workflow](http://eurobarometer.danielantal.eu/articles/workflow.html) are implemented yet.

@@
